Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
citas modificadas

In order to address this problem, remote virtualization was proposed
and several solutions have been presented (e.g. {rCUDA}~\cite{tonithesis,toniparco},
DS-CUDA~\cite{dscuda}, gVirtus~\cite{gvirtus}, vCUDA~\cite{vcuda}, VOCL~\cite{vocl}, and SnuCL~\cite{snucl}).

@@

\section{\uppercase{Background}}
\label{sec:background}
\subsection{The rCUDA Framework}
\label{sec:rcuda}
{rCUDA}~\cite{tonithesis,toniparco} is a middleware that enables transparent access
to any NVIDIA GPU device present in a cluster from all compute
nodes. The GPUs can be accessed and shared between nodes, and a single node can use all these graphic accelerators
as if they were local.
These features are focused in attaining higher accelerator utilization rates in the overall system while simultaneously reducing
resource, space, and energy~\cite{energy14} requirements.
rCUDA is structured following a client-server distributed
architecture: the client middleware is allocated in the same cluster node where the application demanding GPGPU
acceleration services is executed, providing a transparent replacement for the
native CUDA libraries. Furthermore, the server middleware is executed in the
cluster nodes from which the actual GPUs provide the requested GPGPU service.
To support a concurrent scenario where GPUs are shared between
processes\slash nodes, {rCUDA} manages separate device contexts for
each client application.

>>>>

In order to address this problem, remote virtualization was proposed
and several solutions have been presented (e.g. {rCUDA}~\cite{tonithesis},
DS-CUDA~\cite{dscuda}, gVirtus~\cite{gvirtus}, vCUDA~\cite{vcuda}, VOCL~\cite{vocl}, and SnuCL~\cite{snucl}).

@@

\section{\uppercase{Background}}
\label{sec:background}
\subsection{The rCUDA Framework}
\label{sec:rcuda}
{rCUDA}~\cite{toniparco} is a middleware that enables transparent access
to any NVIDIA GPU device present in a cluster from all compute
nodes. The GPUs can be accessed and shared between nodes, and a single node can use all these graphic accelerators
as if they were local.
These features are focused in attaining higher accelerator utilization rates in the overall system while simultaneously reducing
resource, space, and energy~\cite{energy14} requirements.
rCUDA is structured following a client-server distributed
architecture: the client middleware is allocated in the same cluster node where the application demanding GPGPU
acceleration services is executed, providing a transparent replacement for the
native CUDA libraries. Furthermore, the server middleware is executed in the
cluster nodes from which the actual GPUs provide the requested GPGPU service.
To support a concurrent scenario where GPUs are shared between
processes\slash nodes, {rCUDA} manages separate device contexts for
each client application.
